New Computer Fan Data-Science Set-up\\ Python (Anaconda), R (Rstudio), Matlab and Latex (Texlive)\\ Atom, VScode, Pycharm

### 2020-01-03 nontex/install/linux/fn_ubuntu.tex
set up compile minor update

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}

@@

\documentclass[
]{article}

@@

  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex

@@

  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}

@@

% Use upquote if available, for straight quotes in verbatim environments

@@

\IfFileExists{microtype.sty}{% use microtype if available

@@

\@ifundefined{KOMAClassName}{% if non-KOMA class

@@

    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}

@@

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}

@@

% Set default figure placement to htbp
\def\fps@figure{htbp}

@@

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# install atom}
\FunctionTok{sudo}\NormalTok{ apt-get install atom}
\end{Highlighting}
\end{Shaded}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  wget to download from url to download folder
\item
  bash to install
\item
  follow instructions, type yes
\item
  source \textasciitilde/.bashrc
\end{enumerate}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# could be saved in current folder: pwd}
\CommentTok{# could be saved in download folder: ~/Downloads}
\FunctionTok{wget}\NormalTok{ https://repo.anaconda.com/archive/Anaconda3-2019.10-Linux-x86_64.sh}
\CommentTok{# install file}
\FunctionTok{bash} \StringTok{"Anaconda3-2019.10-Linux-x86_64.sh"}
\CommentTok{# refresh}
\BuiltInTok{source}\NormalTok{ ~/.bashrc}
\CommentTok{# show all installed packages under current envir}
\ExtensionTok{conda}\NormalTok{ list}
\CommentTok{# see where key files are installed}
\FunctionTok{which}\NormalTok{ python}
\FunctionTok{which}\NormalTok{ conda}
\CommentTok{# use conda-forge as main channel and update all}
\ExtensionTok{conda}\NormalTok{ config --add channels conda-forge}
\ExtensionTok{conda}\NormalTok{ update --all}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\ExtensionTok{apt-get}\NormalTok{ update}
\ExtensionTok{apt-get}\NormalTok{ install r-base r-base-dev}
\end{Highlighting}
\end{Shaded}

>>>>

\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere

@@

\documentclass[]{article}

@@

  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex

@@

  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}

@@

% use upquote if available, for straight quotes in verbatim environments

@@

% use microtype if available
\IfFileExists{microtype.sty}{%

@@

@@

\setlength{\parskip}{6pt plus 2pt minus 1pt}
}

@@

\usepackage{hyperref}

@@

@@

% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# install atom}
\FunctionTok{sudo}\NormalTok{ apt-get install atom}
\CommentTok{# install various atom packages that are necessary}
\FunctionTok{apm}\NormalTok{ install vim-mode-plus}
\end{Highlighting}
\end{Shaded}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  wget to download from url to download folder
\item
  bash to install
\item
  follow instructions, type yes
\item
  source \textasciitilde{}/.bashrc
\end{enumerate}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# To remove conda Fully}
\FunctionTok{rm}\NormalTok{ -rf ~/anaconda3}

\CommentTok{# could be saved in current folder: pwd}
\CommentTok{# could be saved in download folder: ~/Downloads}
\FunctionTok{wget}\NormalTok{ https://repo.anaconda.com/archive/Anaconda3-2019.10-Linux-x86_64.sh}
\CommentTok{# install file}
\FunctionTok{bash} \StringTok{"Anaconda3-2019.10-Linux-x86_64.sh"}
\CommentTok{# refresh}
\BuiltInTok{source}\NormalTok{ ~/.bashrc}

\CommentTok{# show all installed packages under current envir}
\ExtensionTok{conda}\NormalTok{ list}
\CommentTok{# see where key files are installed}
\FunctionTok{which}\NormalTok{ python}
\FunctionTok{which}\NormalTok{ conda}
\CommentTok{# use conda-forge as main channel and update all}
\ExtensionTok{/*}\NormalTok{ conda config --add channels conda-forge */}
\ExtensionTok{conda}\NormalTok{ update --all}
\end{Highlighting}
\end{Shaded}

Additional statistics and related models to install:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{conda install }\OperatorTok{-}\NormalTok{y statsmodels datashape seaborn}
\CommentTok{# conda install statsmodels}
\CommentTok{# conda install datashape}
\CommentTok{# conda install seaborn}

\NormalTok{conda install }\OperatorTok{-}\NormalTok{c conda}\OperatorTok{-}\NormalTok{forge }\OperatorTok{-}\NormalTok{y interpolation awscli}
\CommentTok{# conda install -c conda-forge interpolation}
\CommentTok{# conda install -c conda-forge awscli}

\NormalTok{conda install }\OperatorTok{-}\NormalTok{c anaconda }\OperatorTok{-}\NormalTok{y boto3}

\CommentTok{# conda install -c r r-irkernel}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Debian R is maintained by Johannes Ranke, copied from https://cran.r-project.org/bin/linux/debian/:}
\ExtensionTok{apt-key}\NormalTok{ adv --keyserver keys.gnupg.net --recv-key }\StringTok{'E19F5F87128899B192B1A2C2AD5F960A256A04AF'}
\CommentTok{# Add to source.list, for debian stretch (9)}
\CommentTok{# sudo su added for security issue as super-user}
\FunctionTok{sudo}\NormalTok{ su -c }\StringTok{"sudo echo 'deb http://cloud.r-project.org/bin/linux/debian stretch-cran35/' >> /etc/apt/sources.list"}
\CommentTok{# if added wrong lines, delete 3rd line}
\FunctionTok{sudo}\NormalTok{ sed }\StringTok{'3d'}\NormalTok{ /etc/apt/sources.list}

\CommentTok{# Update and Install R, should say updated from cloud.r}
\FunctionTok{sudo}\NormalTok{ apt-get update}
\FunctionTok{sudo}\NormalTok{ apt-get install r-base r-base-dev}
\end{Highlighting}
\end{Shaded}

\hypertarget{install-other-programs-and-packages}{%
\section{Install Other Programs and
Packages}\label{install-other-programs-and-packages}}

Other key programs and packages to install.

\begin{itemize}
\tightlist
\item
  vim: faster editor, on lower resource machines, atom is slow and
  typing could feel laggy.
\item
  htop: for resource monitoring
\end{itemize}

\begin{verbatim}
sudo apt-get install vim
sudo apt-get install sublime-text
sudo apt-get install htop
\end{verbatim}

### 2020-01-03 nontex/install/windows/fn_installations.Rmd
set up compile minor update

Press *Ctrl + P*, paste the *ext install* commands below to install extensions. Extensions are in: *%USERPROFILE%\.vscode\extensions* for windows. Can change code for extension there.

@@

```{JSON}
"latex-workshop.view.pdf.external.synctex.command": "C:/Program Files/SumatraPDF/SumatraPDF.exe",
"latex-workshop.view.pdf.external.synctex.args": [
  "-forward-search",
  "%TEX%",
  "%LINE%",
  "-reuse-instance",
  "-inverse-search",
  "code \"C:\\Users\\fan\\AppData\\Local\\Programs\\Microsoft VS Code\\resources\\app\\out\\cli.js\" -r -g \"%f:%l\"",
  "%PDF%",
]
```

>>>>

Press *Ctrl + P*, paste the *ext install* commands below to install extensions. Extensions are in: *%USERPROFILE%/.vscode/extensions* for windows. Can change code for extension there.

@@

```
"latex-workshop.view.pdf.external.synctex.command": "C:/Program Files/SumatraPDF/SumatraPDF.exe",
"latex-workshop.view.pdf.external.synctex.args": [
  "-forward-search",
  "%TEX%",
  "%LINE%",
  "-reuse-instance",
  "-inverse-search",
  "code \"C:\\Users\\fan\\AppData\\Local\\Programs\\Microsoft VS Code\\resources\\app\\out\\cli.js\" -r -g \"%f:%l\"",
  "%PDF%",
]
```

### 2020-01-03 nontex/install/windows/fn_installations.tex
set up compile minor update

@@

@@

\begin{itemize}
\tightlist
\item
  Okular 3 pages per row view:

  \begin{itemize}
  \tightlist
  \item
    view, overview
  \end{itemize}
\item
  Automatic Update when PDF updated elsewhere

  \begin{itemize}
  \tightlist
  \item
    this is one of the key reasons to use okular, when I knit a Rmd file
    to PDF, the currently open Okular PDF file automatically updates and
    does not give file is open error like Acrobat.
  \end{itemize}
\item
  Background color:

  \begin{itemize}
  \tightlist
  \item
    can easily change background color to non-white.
  \end{itemize}
\end{itemize}

@@

@@

VSCode is much more light-weight than Atom, much faster. On Windows,
download \href{https://code.visualstudio.com/download}{here}.

@@

Press \emph{Ctrl + P}, paste the \emph{ext install} commands below to
install extensions:

@@

\hypertarget{vscode-and-latex}{%
\paragraph{VSCode and Latex}\label{vscode-and-latex}}

@@

>>>>

\hypertarget{sumatrapdf}{%
\subsection{SumatraPDF}\label{sumatrapdf}}

For windows, install
\href{https://www.sumatrapdfreader.org/download-free-pdf-viewer.html}{SumatraPDF}.
Can easily modify colors.

\textbf{Settings}

\href{https://medium.com/greatnote/kindle-sepia-color-code-1fed14b1a5ef}{Kindle
Sepia} modifications:

\begin{itemize}
\tightlist
\item
  Background color:

  \begin{itemize}
  \tightlist
  \item
    Kindle Sepia: \emph{fbf0d9}
  \item
    Kindle Sepia Light: \emph{fff8e6}
  \end{itemize}
\item
  Text color:

  \begin{itemize}
  \tightlist
  \item
    Kindle Sepia: \emph{5f4b32}
  \item
    Kindle Sepia Darker: \emph{503f2a}
  \item
    Kindle Sepia Darkerer: \emph{1e170f}
  \end{itemize}
\end{itemize}

\begin{verbatim}
FixedPageUI [
    TextColor = #1e170f
    BackgroundColor = #fff8e6
    SelectionColor = #f5fc0c
    WindowMargin = 2 4 2 4
    PageSpacing = 4 4
]
\end{verbatim}

@@

\textbf{Settings}:

\begin{itemize}
\tightlist
\item
  Background color:

  \begin{itemize}
  \tightlist
  \item
    background behind pdf: configure okular, general, use custom
    backgroun color, Gainsboro gray: \emph{DCDCDC}, kindle sepia:
    \emph{FBF0D9}
  \item
    pdf background itself: configure okular, accessbility, change color,
    change paper color, Light Kindle Sepia: \emph{fff8e6}
  \end{itemize}
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  Okular 3 pages per row view: view, overview
\item
  Automatic Update when PDF updated elsewhere: this is one of the key
  reasons to use okular, when I knit a Rmd file to PDF, the currently
  open Okular PDF file automatically updates and does not give file is
  open error like Acrobat.
\item
  Background color:

  \begin{itemize}
  \tightlist
  \item
    background behind pdf: configure okular, general, use custom
    backgroun color, Gainsboro gray: \emph{DCDCDC}, kindle sepia:
    \emph{FBF0D9}
  \item
    pdf background itself: configure okular, accessbility, change color,
    change paper color, Light Kindle Sepia: \emph{fff8e6}
  \end{itemize}
\end{itemize}

@@

All settings here JSON files here:

\begin{itemize}
\tightlist
\item
  windows: \emph{C:/Users/fan/AppData/Roaming/Code/User}, can be
  modified here directly
\end{itemize}

@@

VSCode is much more light-weight than Atom, much faster. On Windows,
download \href{https://code.visualstudio.com/download}{here}. VScode
settings easy to change for various extensions. Very very good Latex
Editor, probably the best I have used.

@@

Press \emph{Ctrl + P}, paste the \emph{ext install} commands below to
install extensions. Extensions are in:
\emph{\%USERPROFILE\%/.vscode/extensions} for windows. Can change code
for extension there.

@@

\hypertarget{vscode-and-latex}{%
\subsubsection{VSCode and Latex}\label{vscode-and-latex}}

@@

\textbf{Settings}

change background border pdf color (not pdf but border): \emph{ctrl +
shift + x}, LatexWorkshop, Settings, Configure Extension Settings,
Search for background, change color name. or enter:
\emph{latex-workshop.view.pdf.backgroundColor}. use gainsboro gray:
\emph{\#DCDCDC}, or lightgray \emph{\#D3D3D3}.

To take advantage of Okular (where background color can be none-white
for example). Go to settings, and: 1. Change:
\emph{latex-workshop.view.pdf.viewer} to external 2. Change:
\emph{latex-workshop.view.pdf.external.viewer.command} to
\emph{C:/Program Files/SumatraPDF/SumatraPDF.exe} open up
\emph{C:/Users/fan/AppData/Roaming/Code/User/settings.json}, and copy
these in:

\begin{verbatim}
"latex-workshop.view.pdf.external.synctex.command": "C:/Program Files/SumatraPDF/SumatraPDF.exe",
"latex-workshop.view.pdf.external.synctex.args": [
  "-forward-search",
  "%TEX%",
  "%LINE%",
  "-reuse-instance",
  "-inverse-search",
  "code \"C:\\Users\\fan\\AppData\\Local\\Programs\\Microsoft VS Code\\resources\\app\\out\\cli.js\" -r -g \"%f:%l\"",
  "%PDF%",
]
\end{verbatim}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  upon savings, rebuid file and update pdf (similar to overleaf)
\item
  hover offers equation preview
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  preview: \emph{ctrl + alt + v}
\item
  synctex location: \emph{ctrl + alt + j}
\end{enumerate}

\hypertarget{vscode-settings.json}{%
\subsubsection{VSCode settings.json}\label{vscode-settings.json}}

The settings.json file, \emph{\%APPDATA\%/Code/User/settings.json}:

\begin{verbatim}
{
  "r.rterm.windows": "C:/Program Files/R/R-3.6.2/bin/x64/R.exe",
  "window.zoomLevel": 0,
  "latex-workshop.view.pdf.viewer": "external",
  "latex-workshop.view.pdf.external.synctex.command": "C:/Program Files/SumatraPDF/SumatraPDF.exe",
  "latex-workshop.view.pdf.external.synctex.args": [
        "-forward-search",
        "%TEX%",
        "%LINE%",
        "-reuse-instance",
        "-inverse-search",
        "code \"C:\\Users\\fan\\AppData\\Local\\Programs\\Microsoft VS Code\\resources\\app\\out\\cli.js\" -r -g \"%f:%l\"",
        "%PDF%",
    ],
    "latex-workshop.view.pdf.external.viewer.command": "C:/Program Files/SumatraPDF/SumatraPDF.exe"
}
\end{verbatim}
